---
title: "Politician Stock Disclosures"
subtitle: "U.S. House Periodic Transaction Reports"
page-layout: full

format:
  html:
    toc: false

execute:
  echo: false
  warning: false
  message: false
---

<style>

/* =========================================================
   PAGE
   ========================================================= */

.quarto-title-block {
  display: none;
}

.wide-shell {
  width: min(1750px, calc(100vw - 32px));
  margin-left: auto;
  margin-right: auto;
}

.project-main-title {
  margin-bottom: 0.2rem;
}

.project-subtitle {
  font-size: 1.15rem;
  opacity: 0.7;
  margin-bottom: 2rem;
}

.dataTables_wrapper {
  font-size: 0.9rem;
}


/* =========================================================
   CHAMBER TOGGLE
   ========================================================= */

.chamber-toggle {
  display: inline-flex;
  gap: 0.5rem;
  margin-bottom: 1.5rem;
}

.chamber-toggle a,
.chamber-toggle span {
  padding: 0.35rem 0.9rem;

  border: 1px solid #6ea8fe;
  border-radius: 999px;

  font-size: 0.85rem;
  text-decoration: none;
  color: inherit;
}

.chamber-toggle .chamber-active {
  background: rgba(110, 168, 254, 0.18);
  font-weight: 700;
}

.chamber-toggle a:hover {
  background: rgba(110, 168, 254, 0.08);
}

/* Pandoc wraps a bare inline element (a lone <a> or <span>+<a> pair)
   starting a raw-HTML line in a <p>, which carries default browser
   margin and throws off spacing next to elements that don't get
   wrapped (like <button>). Neutralize it here. */
.featured-actions p,
.chamber-toggle p {
  margin: 0;
}


/* =========================================================
   FEATURED PTR
   ========================================================= */

.featured-card {
  display: grid;

  grid-template-columns:
    minmax(560px, 0.9fr)
    minmax(0, 1.1fr);

  border: 1px solid #444;
  border-radius: 10px;
  overflow: hidden;

  margin: 1.25rem 0;
}

.featured-info {
  padding: 1.5rem;
  border-right: 1px solid #444;
}

.featured-info h3 {
  margin: 0 0 1.2rem 0;
}

.featured-meta {
  display: grid;
  gap: 0.65rem;
  margin-bottom: 1.35rem;
}

.featured-meta-row {
  display: grid;
  grid-template-columns: 115px 1fr;
  gap: 0.5rem;
  align-items: baseline;
}

.featured-meta-label {
  font-weight: 700;
}


/* =========================================================
   FEATURED CONTROLS
   ========================================================= */

.featured-controls {
  display: grid;

  grid-template-columns:
    240px minmax(250px, 1fr);

  gap: 1.25rem;

  align-items: start;

  max-width: 590px;

  margin-top: 1rem;
}

.featured-actions {
  display: grid;
  grid-template-columns: 1fr;

  gap: 0.65rem;

  width: 240px;
}

.ptr-button {
  display: flex;

  align-items: center;
  justify-content: center;

  width: 240px;
  height: 44px;

  box-sizing: border-box;

  padding: 0 0.9rem;

  border: 1px solid #6ea8fe;
  border-radius: 6px;

  background: transparent;
  color: inherit;

  text-decoration: none;
  text-align: center;

  white-space: nowrap;

  cursor: pointer;
  font: inherit;

  transition:
    border-color 0.15s ease,
    background 0.15s ease,
    transform 0.15s ease;
}

.ptr-button:hover {
  border-color: #9bc2ff;
  background: rgba(110, 168, 254, 0.08);
  transform: translateY(-1px);
}


/* =========================================================
   FILING ID SEARCH
   ========================================================= */

.filing-search {
  width: 100%;

  padding-left: 1.2rem;

  border-left: 1px solid #444;
}

.filing-search label {
  display: block;

  margin-bottom: 0.55rem;

  font-size: 0.78rem;
  font-weight: 700;

  opacity: 0.75;
}

.filing-search-row {
  display: grid;

  grid-template-columns:
    minmax(0, 1fr) 72px;

  width: 100%;
}

.filing-search-row input {
  width: 100%;
  min-width: 0;

  height: 44px;

  box-sizing: border-box;

  padding: 0 0.7rem;

  border: 1px solid #555;
  border-right: none;

  border-radius: 6px 0 0 6px;

  background: transparent;
  color: inherit;

  font: inherit;
}

.filing-search-row input:focus {
  outline: none;
  border-color: #6ea8fe;
}

.filing-search-row button {
  height: 44px;

  box-sizing: border-box;

  border: 1px solid #6ea8fe;

  border-radius: 0 6px 6px 0;

  background: transparent;
  color: inherit;

  cursor: pointer;

  font: inherit;

  white-space: nowrap;
}

.filing-search-row button:hover {
  background: rgba(110, 168, 254, 0.08);
}

.filing-search-message {
  min-height: 1rem;

  margin-top: 0.45rem;

  font-size: 0.75rem;

  opacity: 0.7;
}


/* =========================================================
   FEATURED EXTRACTION TABLE
   ========================================================= */

.featured-extract {
  padding: 1.5rem;
  min-width: 0;
}

.featured-extract h3 {
  margin: 0 0 1rem 0;
}

.featured-table-wrap {
  width: 100%;
  overflow-x: auto;
}

.featured-table {
  width: 100%;
  border-collapse: collapse;
  font-size: 0.87rem;
}

.featured-table th,
.featured-table td {
  text-align: left;
  vertical-align: top;

  padding: 0.6rem 0.45rem;

  border-bottom: 1px solid #3b3b3b;
}

.featured-table th {
  opacity: 0.7;
  font-size: 0.75rem;
}

.featured-empty {
  opacity: 0.65;
  font-style: italic;
}


/* =========================================================
   PDF VIEWER
   ========================================================= */

.ptr-pdf-section {
  margin: 1.5rem 0 3rem 0;
}

.ptr-pdf-header {
  margin-bottom: 0.8rem;
}

.ptr-pdf-header h3 {
  margin: 0;
}

.ptr-pdf-viewer {
  display: block;

  width: 100%;
  height: 2200px;

  border: 1px solid #444;
  border-radius: 8px;

  background: #181818;
}

.pdf-fallback {
  padding: 1rem;
}


/* =========================================================
   EXPLORE SUMMARY
   ========================================================= */

.explore-stats {
  display: grid;

  grid-template-columns:
    repeat(4, 1fr);

  margin: 1.5rem 0 2rem 0;

  border-top: 1px solid #3b3b3b;
  border-bottom: 1px solid #3b3b3b;
}

.explore-stat {
  padding: 1.2rem 1.4rem;

  border-right: 1px solid #3b3b3b;
}

.explore-stat:last-child {
  border-right: none;
}

.explore-stat-label {
  font-size: 0.72rem;

  text-transform: uppercase;

  letter-spacing: 0.08em;

  opacity: 0.55;

  margin-bottom: 0.35rem;
}

.explore-stat-number {
  font-size: 1.8rem;
  font-weight: 700;
  line-height: 1;
}


/* =========================================================
   SUBTLE DEBUG TOGGLE
   ========================================================= */

.debug-control {
  display: none;

  clear: left;

  margin-top: 0.25rem;
  margin-bottom: 0.5rem;

  font-size: 0.72rem;
}

.debug-toggle {
  display: inline-flex;

  align-items: center;

  gap: 0.4rem;

  margin: 0;

  cursor: pointer;

  opacity: 0.65;

  transition: opacity 0.15s ease;
}

.debug-toggle:hover {
  opacity: 1;
}

.debug-toggle input {
  width: 13px;
  height: 13px;

  margin: 0;

  cursor: pointer;

  accent-color: #6ea8fe;
}

.debug-toggle strong {
  font-size: 0.72rem;
  font-weight: 600;
}

.debug-toggle span {
  opacity: 0.7;
}


/* High-QA rows in debug mode */
table.dataTable tbody tr.qa-high-row td {
  background: rgba(214, 153, 52, 0.10);
}

.qa-high-badge {
  display: inline-block;

  padding: 0.1rem 0.35rem;

  border: 1px solid rgba(214, 153, 52, 0.65);
  border-radius: 999px;

  background: rgba(214, 153, 52, 0.10);

  font-size: 0.68rem;
  font-weight: 700;

  text-transform: uppercase;
}


/* =========================================================
   RESPONSIVE
   ========================================================= */

@media (max-width: 1150px) {

  .featured-card {
    grid-template-columns: 1fr;
  }

  .featured-info {
    border-right: none;
    border-bottom: 1px solid #444;
  }

  .ptr-pdf-viewer {
    height: 1500px;
  }
}

@media (max-width: 700px) {

  .wide-shell {
    width: calc(100vw - 24px);
  }

  .featured-controls {
    grid-template-columns: 1fr;
  }

  .featured-actions {
    width: 100%;
  }

  .ptr-button {
    width: 100%;
  }

  .filing-search {
    padding-left: 0;
    padding-top: 1rem;

    border-left: none;
    border-top: 1px solid #444;
  }

  .explore-stats {
    grid-template-columns: repeat(2, 1fr);
  }

  .ptr-pdf-viewer {
    height: 1100px;
  }
}

@media (max-width: 500px) {

  .explore-stats {
    grid-template-columns: 1fr;
  }

  .explore-stat {
    border-right: none;
  }

  .featured-meta-row {
    grid-template-columns: 1fr;
    gap: 0;
  }

  .ptr-pdf-viewer {
    height: 900px;
  }
}

</style>


```{r}
library(readr)
library(dplyr)
library(DT)
library(jsonlite)


# The automated house-ptr-scraper repo is the source of truth once its
# pipeline is live. Locally it's a true sibling folder (two levels up from
# projects/); in CI, actions/checkout can't check out a repo outside
# $GITHUB_WORKSPACE via "..", so the deploy workflow nests it inside this
# repo's checkout instead (one level up). The static snapshot committed to
# this repo (data/house_ptr_transactions_web.csv) is the last-resort
# fallback if neither is present yet.
data_path_candidates <- c(
  "../../house-ptr-scraper/data/06_public/house_ptr_transactions_web.csv",
  "../house-ptr-scraper/data/06_public/house_ptr_transactions_web.csv",
  "../data/house_ptr_transactions_web.csv"
)

data_path <- data_path_candidates[file.exists(data_path_candidates)][1]


ptr <- read_csv(
  data_path,
  show_col_types = FALSE
)


if (!"amount_min" %in% names(ptr)) {
  ptr$amount_min <- NA_real_
}


if (!"amount_max" %in% names(ptr)) {
  ptr$amount_max <- NA_real_
}


ptr_prepared <- ptr |>
  mutate(

    filing_id =
      as.character(
        filing_id
      ),

    parsed_transaction_date =
      as.Date(
        transaction_date,
        format = "%Y-%m-%d"
      ),

    qa_norm =
      tolower(
        trimws(
          coalesce(
            review_level,
            ""
          )
        )
      ),

    owner_display =
      case_when(

        is.na(owner) |
          trimws(owner) == "" ~
            "Self",

        toupper(
          trimws(owner)
        ) == "SP" ~
          "Spouse",

        toupper(
          trimws(owner)
        ) == "JT" ~
          "Joint",

        toupper(
          trimws(owner)
        ) == "DC" ~
          "Dependent child",

        TRUE ~
          owner
      ),

    amount_min_num =
      suppressWarnings(
        as.numeric(
          gsub(
            "[^0-9.]",
            "",
            as.character(
              amount_min
            )
          )
        )
      ),

    amount_max_num =
      suppressWarnings(
        as.numeric(
          gsub(
            "[^0-9.]",
            "",
            as.character(
              amount_max
            )
          )
        )
      ),

    amount_display =
      case_when(

        !is.na(amount_category) &
          trimws(amount_category) != "" ~
            amount_category,

        !is.na(amount_max_num) &
          amount_max_num <= 1000 ~
            paste0(
              "Up to $",
              format(
                amount_max_num,
                big.mark = ",",
                scientific = FALSE,
                trim = TRUE
              )
            ),

        !is.na(amount_min_num) &
          !is.na(amount_max_num) ~
            paste0(
              "$",
              format(
                amount_min_num,
                big.mark = ",",
                scientific = FALSE,
                trim = TRUE
              ),
              " - $",
              format(
                amount_max_num,
                big.mark = ",",
                scientific = FALSE,
                trim = TRUE
              )
            ),

        !is.na(amount_max_num) ~
          paste0(
            "Up to $",
            format(
              amount_max_num,
              big.mark = ",",
              scientific = FALSE,
              trim = TRUE
            )
          ),

        TRUE ~
          ""
      )

  )
```


::: {.column-screen}

::: {.wide-shell}


# Politician Stock Disclosures {.project-main-title}

<div class="project-subtitle">U.S. House Periodic Transaction Reports</div>

<div class="chamber-toggle">
<span class="chamber-active">House</span>
<a href="stock-disclosures-senate.qmd">Senate</a>
</div>


This project turns official U.S. House **Periodic Transaction Report (PTR)** disclosures into structured transaction data that can be searched and analyzed.


## Featured PTR


This section randomly selects one successfully extracted House filing from the dataset.

Use **Show another PTR** to pick another clean example, or enter a **Filing ID** to inspect a specific source disclosure.


```{r}
filing_summary <- ptr_prepared |>
  group_by(
    filing_id,
    source_year,
    politician,
    state_district,
    original_pdf_url
  ) |>
  summarise(

    transaction_count =
      n(),

    any_high_review =
      any(
        qa_norm == "high"
      ),

    all_dates_valid =
      all(
        !is.na(
          parsed_transaction_date
        ) &
          parsed_transaction_date >=
            as.Date("2021-01-01") &
          parsed_transaction_date <=
            Sys.Date()
      ),

    .groups =
      "drop"
  ) |>
  filter(

    !is.na(filing_id),
    filing_id != "",

    !is.na(source_year),

    !is.na(politician),
    politician != "",

    !is.na(original_pdf_url),
    original_pdf_url != ""

  )


if (
  nrow(
    filing_summary
  ) == 0
) {

  stop(
    "No PTR filings were found."
  )
}


featured_items <- lapply(

  seq_len(
    nrow(
      filing_summary
    )
  ),

  function(i) {

    filing_info <-
      filing_summary[
        i,
        ,
        drop = FALSE
      ]


    filing_rows <-
      ptr_prepared |>
      filter(

        filing_id ==
          filing_info$filing_id[[1]],

        source_year ==
          filing_info$source_year[[1]]

      ) |>
      arrange(

        desc(
          parsed_transaction_date
        )

      ) |>
      transmute(

        Owner =
          owner_display,

        Asset =
          asset_v8_2_cleaned,

        Ticker =
          ticker_v8_2_cleaned,

        Type =
          transaction_type,

        Date =
          transaction_date,

        Amount =
          amount_display

      )


    list(

      politician =
        filing_info$politician[[1]],

      district =
        filing_info$state_district[[1]],

      filing_id =
        filing_info$filing_id[[1]],

      year =
        as.character(
          filing_info$source_year[[1]]
        ),

      pdf_url =
        filing_info$original_pdf_url[[1]],

      transaction_count =
        nrow(
          filing_rows
        ),

      eligible_random =
        (
          !filing_info$any_high_review[[1]] &&
          filing_info$all_dates_valid[[1]]
        ),

      transactions =
        filing_rows

    )
  }
)


featured_json <- toJSON(
  featured_items,
  auto_unbox = TRUE,
  dataframe = "rows",
  na = "null"
)
```


<div class="featured-card">

<div class="featured-info">

<h3 id="featured-name"></h3>

<div class="featured-meta">

<div class="featured-meta-row"><span class="featured-meta-label">District</span><span id="featured-district"></span></div>

<div class="featured-meta-row"><span class="featured-meta-label">Filing ID</span><span id="featured-filing-id"></span></div>

<div class="featured-meta-row"><span class="featured-meta-label">Source year</span><span id="featured-year"></span></div>

<div class="featured-meta-row"><span class="featured-meta-label">Transactions</span><span id="featured-count"></span></div>

</div>


<div class="featured-controls">

<div class="featured-actions">
<button type="button" class="ptr-button" id="random-ptr-button">Show another PTR</button>
<a class="ptr-button" id="featured-pdf-link" href="#" target="_blank" rel="noopener">Open original House PDF</a>
</div>

<div class="filing-search">
<label for="filing-id-search">Find by Filing ID</label>
<div class="filing-search-row"><input id="filing-id-search" type="text" inputmode="numeric" placeholder="e.g. 20020359"><button id="filing-id-search-button" type="button">Load</button></div>
<div id="filing-search-message" class="filing-search-message"></div>
</div>

</div>

</div>


<div class="featured-extract">

<h3>Extracted transactions</h3>

<div class="featured-table-wrap">

<table class="featured-table">

<thead>
<tr>
<th>Owner</th>
<th>Asset</th>
<th>Ticker</th>
<th>Type</th>
<th>Date</th>
<th>Amount</th>
</tr>
</thead>

<tbody id="featured-table-body"></tbody>

</table>

</div>

</div>

</div>


<div class="ptr-pdf-section">

<div class="ptr-pdf-header">
<h3>Original House PTR</h3>
</div>

<object id="featured-pdf-viewer" class="ptr-pdf-viewer" type="application/pdf">

<div class="pdf-fallback">

Your browser could not display this PDF inline.

<a id="featured-pdf-fallback-link" href="#" target="_blank" rel="noopener">Open the original House PDF</a>

</div>

</object>

</div>


```{r, results='asis'}
cat(
  '<script>',
  'const allFeaturedPTRs = ',
  featured_json,
  ';',
  '</script>'
)
```


<script>

(function () {

  let currentIndex = -1;


  function cleanValue(value) {

    if (
      value === null ||
      value === undefined ||
      value === "NA"
    ) {

      return "";
    }

    return String(value);
  }


  const eligibleRandomIndices =
    allFeaturedPTRs
      .map(
        function(item, index) {

          return item.eligible_random
            ? index
            : null;
        }
      )
      .filter(
        function(index) {

          return index !== null;
        }
      );


  function randomIndex() {

    const pool =
      eligibleRandomIndices.length > 0
        ? eligibleRandomIndices
        : allFeaturedPTRs.map(
            function(item, index) {

              return index;
            }
          );


    if (
      pool.length <= 1
    ) {

      return pool[0];
    }


    let nextIndex;


    do {

      nextIndex =
        pool[
          Math.floor(
            Math.random() *
            pool.length
          )
        ];

    } while (
      nextIndex === currentIndex
    );


    return nextIndex;
  }


  function updatePDF(url) {

    const viewer =
      document.getElementById(
        "featured-pdf-viewer"
      );

    const mainLink =
      document.getElementById(
        "featured-pdf-link"
      );

    const fallbackLink =
      document.getElementById(
        "featured-pdf-fallback-link"
      );


    mainLink.href = url;
    fallbackLink.href = url;


    viewer.removeAttribute(
      "data"
    );


    window.setTimeout(
      function() {

        viewer.setAttribute(
          "data",
          url +
          "#page=1&zoom=page-fit"
        );

      },
      20
    );
  }


  function renderFeaturedPTR(index) {

    currentIndex = index;


    const item =
      allFeaturedPTRs[
        index
      ];


    document
      .getElementById(
        "featured-name"
      )
      .textContent =
        cleanValue(
          item.politician
        );


    document
      .getElementById(
        "featured-district"
      )
      .textContent =
        cleanValue(
          item.district
        );


    document
      .getElementById(
        "featured-filing-id"
      )
      .textContent =
        cleanValue(
          item.filing_id
        );


    document
      .getElementById(
        "featured-year"
      )
      .textContent =
        cleanValue(
          item.year
        );


    document
      .getElementById(
        "featured-count"
      )
      .textContent =
        Number(
          item.transaction_count
        ).toLocaleString();


    document
      .getElementById(
        "filing-id-search"
      )
      .value =
        cleanValue(
          item.filing_id
        );


    document
      .getElementById(
        "filing-search-message"
      )
      .textContent =
        "";


    const tbody =
      document.getElementById(
        "featured-table-body"
      );


    tbody.innerHTML =
      "";


    let transactions =
      item.transactions;


    if (
      transactions &&
      !Array.isArray(
        transactions
      )
    ) {

      transactions = [
        transactions
      ];
    }


    if (
      !transactions ||
      transactions.length === 0
    ) {

      const row =
        document.createElement(
          "tr"
        );


      const cell =
        document.createElement(
          "td"
        );


      cell.colSpan = 6;

      cell.className =
        "featured-empty";


      cell.textContent =
        "No extracted transaction rows.";


      row.appendChild(
        cell
      );


      tbody.appendChild(
        row
      );

    } else {


      transactions.forEach(
        function(transaction) {


          const row =
            document.createElement(
              "tr"
            );


          const values = [
            transaction.Owner,
            transaction.Asset,
            transaction.Ticker,
            transaction.Type,
            transaction.Date,
            transaction.Amount
          ];


          values.forEach(
            function(value) {


              const cell =
                document.createElement(
                  "td"
                );


              cell.textContent =
                cleanValue(
                  value
                );


              row.appendChild(
                cell
              );
            }
          );


          tbody.appendChild(
            row
          );
        }
      );
    }


    updatePDF(
      item.pdf_url
    );
  }


  function showRandomPTR() {

    const index =
      randomIndex();


    renderFeaturedPTR(
      index
    );
  }


  function loadFilingID() {

    const input =
      document.getElementById(
        "filing-id-search"
      );


    const message =
      document.getElementById(
        "filing-search-message"
      );


    const requestedID =
      input.value
        .trim()
        .replace(
          /\D/g,
          ""
        );


    if (
      !requestedID
    ) {

      message.textContent =
        "Enter a Filing ID.";


      return;
    }


    const index =
      allFeaturedPTRs.findIndex(
        function(item) {


          return String(
            item.filing_id
          ) === requestedID;
        }
      );


    if (
      index === -1
    ) {

      message.textContent =
        "Filing ID not found in this dataset.";


      return;
    }


    message.textContent =
      "";


    renderFeaturedPTR(
      index
    );
  }


  function initializePTRFeature() {

    const randomButton =
      document.getElementById(
        "random-ptr-button"
      );


    const searchButton =
      document.getElementById(
        "filing-id-search-button"
      );


    const searchInput =
      document.getElementById(
        "filing-id-search"
      );


    randomButton.addEventListener(
      "click",
      showRandomPTR
    );


    searchButton.addEventListener(
      "click",
      loadFilingID
    );


    searchInput.addEventListener(
      "keydown",
      function(event) {


        if (
          event.key === "Enter"
        ) {

          loadFilingID();
        }
      }
    );


    showRandomPTR();
  }


  if (
    document.readyState === "loading"
  ) {

    document.addEventListener(
      "DOMContentLoaded",
      initializePTRFeature
    );

  } else {

    initializePTRFeature();
  }

})();

</script>


---


## Explore the transactions


```{r}
explore_all <-
  ptr_prepared |>
  filter(

    !is.na(
      parsed_transaction_date
    ),

    parsed_transaction_date >=
      as.Date("2021-01-01"),

    parsed_transaction_date <=
      Sys.Date()

  ) |>
  arrange(

    desc(
      parsed_transaction_date
    )

  )


explore_clean <-
  explore_all |>
  filter(
    qa_norm != "high"
  )


representatives_count <-
  n_distinct(

    explore_clean$politician[
      !is.na(
        explore_clean$politician
      ) &
      explore_clean$politician != ""
    ]

  )


assets_count <-
  n_distinct(

    explore_clean$asset_v8_2_cleaned[
      !is.na(
        explore_clean$asset_v8_2_cleaned
      ) &
      explore_clean$asset_v8_2_cleaned != ""
    ]

  )


disclosures_count <-
  n_distinct(

    explore_clean$filing_id[
      !is.na(
        explore_clean$filing_id
      ) &
      explore_clean$filing_id != ""
    ]

  )


transactions_count <-
  nrow(
    explore_clean
  )
```


```{r, results='asis'}
cat(

  '<div class="explore-stats">',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Representatives</div>',
  '<div class="explore-stat-number count-up" data-target="',
  representatives_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Assets</div>',
  '<div class="explore-stat-number count-up" data-target="',
  assets_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Disclosures</div>',
  '<div class="explore-stat-number count-up" data-target="',
  disclosures_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Transactions</div>',
  '<div class="explore-stat-number count-up" data-target="',
  transactions_count,
  '">0</div>',
  '</div>',

  '</div>'

)
```


<script>

document.addEventListener(
  "DOMContentLoaded",
  function() {

    const statSection =
      document.querySelector(
        ".explore-stats"
      );


    if (
      !statSection
    ) {

      return;
    }


    let hasAnimated =
      false;


    function animateValue(
      element
    ) {

      const target =
        Number(
          element.dataset.target
        );


      const duration =
        4000;


      const startTime =
        performance.now();


      function update(
        currentTime
      ) {

        const elapsed =
          currentTime -
          startTime;


        const progress =
          Math.min(
            elapsed /
            duration,
            1
          );


        const eased =
          Math.pow(
            progress,
            2.5
          );


        const value =
          Math.floor(
            target *
            eased
          );


        element.textContent =
          value.toLocaleString();


        if (
          progress < 1
        ) {

          requestAnimationFrame(
            update
          );

        } else {

          element.textContent =
            target.toLocaleString();
        }
      }


      requestAnimationFrame(
        update
      );
    }


    const observer =
      new IntersectionObserver(
        function(entries) {

          entries.forEach(
            function(entry) {

              if (
                entry.isIntersecting &&
                !hasAnimated
              ) {

                hasAnimated =
                  true;


                document
                  .querySelectorAll(
                    ".count-up"
                  )
                  .forEach(
                    animateValue
                  );


                observer.disconnect();
              }
            }
          );
        },

        {
          threshold: 0.35
        }
      );


    observer.observe(
      statSection
    );
  }
);

</script>


The table defaults to cleaned records suitable for analysis. High-QA records can be included using the debug control beneath the table.

Use the global search box or individual column filters to search by filing ID, politician, ticker, asset, district, transaction type, or date.


<div id="debug-control" class="debug-control">
<label class="debug-toggle" for="debug-mode-toggle"><input type="checkbox" id="debug-mode-toggle"><strong>Debug mode</strong><span>Include high-QA records</span></label>
</div>


```{r}
display_data <-
  explore_all |>
  transmute(

    `Filing ID` =
      filing_id,

    Politician =
      politician,

    District =
      state_district,

    `Transaction date` =
      transaction_date,

    `Notification date` =
      notification_date,

    Owner =
      owner_display,

    Asset =
      asset_v8_2_cleaned,

    Ticker =
      ticker_v8_2_cleaned,

    Type =
      transaction_type,

    Amount =
      amount_display,

    `QA review` =
      qa_norm,

    `House PDF` =
      original_pdf_url

  )


datatable(

  display_data,

  filter =
    "top",

  rownames =
    FALSE,

  width =
    "100%",

  callback =
    JS(

      "var checkbox = document.getElementById('debug-mode-toggle');",

      "var debugControl = document.getElementById('debug-control');",

      "var wrapper = $(table.table().container());",

      "var info = wrapper.find('.dataTables_info');",

      "if (debugControl && info.length) {",

      "  $(debugControl).insertAfter(info);",

      "  $(debugControl).show();",

      "}",

      "function applyDebugMode() {",

      "  if (!checkbox) return;",

      "  if (checkbox.checked) {",

      "    table.column(10).visible(true);",

      "    table.column(10).search('', true, false, true);",

      "    table.draw();",

      "  } else {",

      "    table.column(10).search('^(?!high$).*$', true, false, true);",

      "    table.column(10).visible(false);",

      "    table.draw();",

      "  }",

      "}",

      "if (checkbox) {",

      "  checkbox.addEventListener('change', applyDebugMode);",

      "  applyDebugMode();",

      "}"

    ),

  options =
    list(

      pageLength =
        10,

      lengthMenu =
        c(
          10,
          25,
          50,
          100
        ),

      scrollX =
        TRUE,

      scrollCollapse =
        TRUE,

      autoWidth =
        TRUE,

      order =
        list(
          list(
            3,
            "desc"
          )
        ),

      rowCallback =
        JS(

          "function(row, data) {",

          "  var qa = String(data[10] || '').toLowerCase().trim();",

          "  if (qa === 'high') {",

          "    $(row).addClass('qa-high-row');",

          "  } else {",

          "    $(row).removeClass('qa-high-row');",

          "  }",

          "}"

        ),

      columnDefs =
        list(

          list(

            targets =
              10,

            visible =
              FALSE,

            render =
              JS(

                "function(data, type, row, meta) {",

                "  if (type !== 'display') return data;",

                "  if (!data) return '';",

                "  if (String(data).toLowerCase().trim() === 'high') {",

                "    return '<span class=\"qa-high-badge\">High</span>';",

                "  }",

                "  return data;",

                "}"

              )

          ),

          list(

            targets =
              11,

            orderable =
              FALSE,

            render =
              JS(

                "function(data, type, row, meta) {",

                "  if (type !== 'display') return data;",

                "  if (!data) return '';",

                "  return '<a href=\"' + data + '\" target=\"_blank\" rel=\"noopener\">View PDF</a>';",

                "}"

              )

          )

        )

    )

)
```


## Data source


The source records are official U.S. House Periodic Transaction Reports.

Each displayed transaction retains the original House disclosure URL when available.


:::

:::