---
title: "Politician Stock Disclosures"
subtitle: "U.S. House Periodic Transaction Reports"
page-layout: full

resources:
  - projects/assets/featured-ptr.pdf

format:
  html:
    toc: false

execute:
  echo: false
  warning: false
  message: false
  execute-dir: project
---

<style>
.dataTables_wrapper {
  font-size: 0.9rem;
}

/* Featured PTR information card */
.ptr-feature {
  border: 1px solid #444;
  border-radius: 10px;
  padding: 1.5rem;
  margin: 1rem 0 1.5rem 0;
}

.ptr-feature h3 {
  margin-top: 0;
}

.ptr-button {
  display: inline-block;
  padding: 0.55rem 0.9rem;
  border: 1px solid #6ea8fe;
  border-radius: 6px;
  text-decoration: none;
  margin-top: 0.5rem;
}

/* Embedded PDF */
.ptr-pdf {
  width: 100%;
  margin: 1.5rem 0 2rem 0;
}

.ptr-pdf iframe {
  width: 100%;
  min-height: 850px;
  border: 1px solid #444;
  border-radius: 8px;
  background: white;
}
</style>

```{r}
library(readr)
library(dplyr)
library(DT)
library(jsonlite)

data_path <- "G:/My Drive/Congressional Trading Data/House_PTRs/07 Public Website Data/house_ptr_transactions_web.csv"

metadata_path <- "G:/My Drive/Congressional Trading Data/House_PTRs/07 Public Website Data/house_ptr_metadata.json"

ptr <- read_csv(
  data_path,
  show_col_types = FALSE
)

meta <- fromJSON(metadata_path)
```

This project turns official U.S. House **Periodic Transaction Report (PTR)** disclosures into structured transaction data that can be searched and analyzed.

## Featured PTR

The page selects one successfully extracted House disclosure as an example of how the original PTR becomes structured transaction data.

The example changes once per day when the site is rebuilt.

```{r}
# Create a real Date variable so malformed dates do not get selected.

candidate_rows <- ptr |>
  mutate(
    parsed_transaction_date = as.Date(
      transaction_date,
      format = "%Y-%m-%d"
    )
  ) |>
  filter(
    !is.na(filing_id),
    !is.na(source_year),
    !is.na(original_pdf_url),
    original_pdf_url != "",
    !is.na(parsed_transaction_date),
    parsed_transaction_date >= as.Date("2021-01-01"),
    parsed_transaction_date <= Sys.Date()
  )

# Summarize by PTR filing.
# Only use filings that contain no rows marked high QA review.

candidate_filings <- candidate_rows |>
  group_by(
    filing_id,
    source_year,
    politician,
    state_district,
    original_pdf_url
  ) |>
  summarise(
    transactions = n(),
    all_non_high_review = all(
      is.na(review_level) | review_level != "high"
    ),
    .groups = "drop"
  ) |>
  filter(all_non_high_review)

if (nrow(candidate_filings) == 0) {
  stop("No suitable featured PTR filings were found.")
}

# The date is used as the seed so the example changes once per day,
# rather than changing every time the document is previewed.

set.seed(as.integer(Sys.Date()))

featured_info <- candidate_filings |>
  slice_sample(n = 1)

featured <- ptr |>
  filter(
    filing_id == featured_info$filing_id[[1]],
    source_year == featured_info$source_year[[1]]
  )

featured_pdf_url <- featured_info$original_pdf_url[[1]]
featured_name <- featured_info$politician[[1]]
featured_district <- featured_info$state_district[[1]]
featured_id <- featured_info$filing_id[[1]]
featured_year <- featured_info$source_year[[1]]
```

```{r}
# Locate the matching PDF in the existing Google Drive archive.

pdf_source <- file.path(
  "G:/My Drive/Congressional Trading Data/House_PTRs/01 Official House PTR PDFs",
  as.character(featured_year),
  paste0(featured_id, ".pdf")
)

# Because this Quarto page lives inside projects/,
# place its public PDF in projects/assets/.

dir.create(
  "projects/assets",
  showWarnings = FALSE,
  recursive = TRUE
)

pdf_destination <- "projects/assets/featured-ptr.pdf"

if (!file.exists(pdf_source)) {
  stop(
    paste(
      "Featured PTR PDF was not found at:",
      pdf_source
    )
  )
}

invisible(
  file.copy(
    pdf_source,
    pdf_destination,
    overwrite = TRUE
  )
)
```

```{r, results='asis'}
cat(
  '<div class="ptr-feature">',

  '<h3>',
  featured_name,
  '</h3>',

  '<p>',

  '<strong>District:</strong> ',
  featured_district,
  '<br>',

  '<strong>Disclosure ID:</strong> ',
  featured_id,
  '<br>',

  '<strong>Source year:</strong> ',
  featured_year,
  '<br>',

  '<strong>Transactions extracted:</strong> ',
  nrow(featured),

  '</p>',

  '<a class="ptr-button" href="',
  featured_pdf_url,
  '" target="_blank" rel="noopener">',
  'Open official House PDF',
  '</a>',

  '</div>',

  '<div class="ptr-pdf">',

  '<iframe ',
  'src="assets/featured-ptr.pdf#view=FitH" ',
  'title="Featured House PTR" ',
  'width="100%" ',
  'height="850px">',

  '</iframe>',

  '</div>'
)
```

### Extracted transactions from this PTR

```{r}
featured_table <- featured |>
  transmute(
    Owner = owner,
    Asset = asset_v8_2_cleaned,
    Ticker = ticker_v8_2_cleaned,
    Type = transaction_type,
    `Transaction date` = transaction_date,
    Amount = amount_category,
    `QA review` = review_level
  )

datatable(
  featured_table,
  rownames = FALSE,
  filter = "none",
  options = list(
    dom = "t",
    paging = FALSE,
    ordering = FALSE,
    autoWidth = TRUE
  )
)
```

The original disclosure above is the source document. The table beneath it shows the structured transaction records extracted from that same PTR.

---

## Explore the transactions

The searchable table below contains the structured transaction records produced from the House PTR archive.

For the public-facing table, rows marked **high QA review** are excluded, malformed dates are removed, and the newest valid transactions appear first.

Use the search box or column filters to look for a politician, ticker, asset, district, transaction type, or date.

::: {.column-page}

```{r}
display_data <- ptr |>
  mutate(
    parsed_transaction_date = as.Date(
      transaction_date,
      format = "%Y-%m-%d"
    )
  ) |>
  filter(
    is.na(review_level) | review_level != "high",
    !is.na(parsed_transaction_date),
    parsed_transaction_date >= as.Date("2021-01-01"),
    parsed_transaction_date <= Sys.Date()
  ) |>
  arrange(
    desc(parsed_transaction_date)
  ) |>
  transmute(
    Politician = politician,
    District = state_district,
    `Transaction date` = transaction_date,
    `Notification date` = notification_date,
    Owner = owner,
    Asset = asset_v8_2_cleaned,
    Ticker = ticker_v8_2_cleaned,
    Type = transaction_type,
    Amount = amount_category,
    `QA review` = review_level,
    `House PDF` = ifelse(
      is.na(original_pdf_url) | original_pdf_url == "",
      "",
      paste0(
        '<a href="',
        original_pdf_url,
        '" target="_blank" rel="noopener">',
        'View PDF',
        '</a>'
      )
    )
  )

datatable(
  display_data,
  filter = "top",
  rownames = FALSE,
  escape = FALSE,
  width = "100%",
  options = list(
    pageLength = 10,
    lengthMenu = c(10, 25, 50, 100),
    scrollX = TRUE,
    scrollCollapse = TRUE,
    autoWidth = TRUE,
    searchHighlight = TRUE,

    # Third displayed column is Transaction date.
    # DataTables uses zero-based column numbering.
    order = list(
      list(2, "desc")
    )
  )
)
```

:::

## Data source

The source records are official U.S. House Periodic Transaction Reports.

Each displayed transaction retains the original House disclosure URL when available.