---
title: "Politician Stock Disclosures"
subtitle: "U.S. House Periodic Transaction Reports"
page-layout: full

format:
  html:
    toc: false

execute:
  echo: false
  warning: false
  message: false
---

<style>
.dataTables_wrapper {
  font-size: 0.9rem;
}

/* Featured PTR */
.ptr-feature {
  border: 1px solid #444;
  border-radius: 10px;
  padding: 1.5rem;
  margin: 1rem 0 1.5rem 0;
}

.ptr-feature h3 {
  margin-top: 0;
}

.ptr-button {
  display: inline-block;
  padding: 0.55rem 0.9rem;
  border: 1px solid #6ea8fe;
  border-radius: 6px;
  text-decoration: none;
  margin-top: 0.5rem;
}

/* Embedded PTR */
.ptr-pdf {
  width: 100%;
  margin: 1.5rem 0 2rem 0;
}

.ptr-pdf iframe {
  width: 100%;
  min-height: 850px;
  border: 1px solid #444;
  border-radius: 8px;
  background: white;
}

/* Clean summary bar */
.explore-stats {
  display: grid;
  grid-template-columns: repeat(4, 1fr);
  margin: 1.5rem 0 2rem 0;
  border-top: 1px solid #3b3b3b;
  border-bottom: 1px solid #3b3b3b;
}

.explore-stat {
  padding: 1.2rem 1.4rem;
  border-right: 1px solid #3b3b3b;
}

.explore-stat:last-child {
  border-right: none;
}

.explore-stat-label {
  font-size: 0.72rem;
  text-transform: uppercase;
  letter-spacing: 0.08em;
  opacity: 0.55;
  margin-bottom: 0.35rem;
}

.explore-stat-number {
  font-size: 1.8rem;
  font-weight: 700;
  line-height: 1;
}

/* Responsive stats */
@media (max-width: 800px) {
  .explore-stats {
    grid-template-columns: repeat(2, 1fr);
  }

  .explore-stat:nth-child(2) {
    border-right: none;
  }

  .explore-stat {
    border-bottom: 1px solid #3b3b3b;
  }
}

@media (max-width: 500px) {
  .explore-stats {
    grid-template-columns: 1fr;
  }

  .explore-stat {
    border-right: none;
  }
}
</style>

```{r}
library(readr)
library(dplyr)
library(DT)

data_path <- "G:/My Drive/Congressional Trading Data/House_PTRs/07 Public Website Data/house_ptr_transactions_web.csv"

ptr <- read_csv(
  data_path,
  show_col_types = FALSE
)
```

::: {.column-page}

This project turns official U.S. House **Periodic Transaction Report (PTR)** disclosures into structured transaction data that can be searched and analyzed.

## Featured PTR

The page selects one successfully extracted House disclosure as an example of how the original PTR becomes structured transaction data.

The example changes once per day when the site is rebuilt.

```{r}
featured_pool <- ptr |>
  mutate(
    parsed_transaction_date = as.Date(
      transaction_date,
      format = "%Y-%m-%d"
    ),
    qa_norm = tolower(
      trimws(
        coalesce(review_level, "")
      )
    )
  ) |>
  group_by(
    filing_id,
    source_year,
    politician,
    state_district,
    original_pdf_url
  ) |>
  summarise(
    transactions = n(),

    any_high_review = any(
      qa_norm == "high"
    ),

    has_valid_date = any(
      !is.na(parsed_transaction_date) &
      parsed_transaction_date >= as.Date("2021-01-01") &
      parsed_transaction_date <= Sys.Date()
    ),

    .groups = "drop"
  ) |>
  filter(
    !is.na(filing_id),
    !is.na(source_year),
    !is.na(original_pdf_url),
    original_pdf_url != "",
    !any_high_review,
    has_valid_date
  )

if (nrow(featured_pool) == 0) {
  stop("No suitable featured PTR filings were found.")
}

set.seed(as.integer(Sys.Date()))

featured_info <- featured_pool |>
  slice_sample(n = 1)

featured <- ptr |>
  filter(
    filing_id == featured_info$filing_id[[1]],
    source_year == featured_info$source_year[[1]]
  )

featured_pdf_url <- featured_info$original_pdf_url[[1]]
featured_name <- featured_info$politician[[1]]
featured_district <- featured_info$state_district[[1]]
featured_id <- featured_info$filing_id[[1]]
featured_year <- featured_info$source_year[[1]]
```

```{r, results='asis'}
cat(
  '<div class="ptr-feature">',

  '<h3>',
  featured_name,
  '</h3>',

  '<p>',

  '<strong>District:</strong> ',
  featured_district,
  '<br>',

  '<strong>Disclosure ID:</strong> ',
  featured_id,
  '<br>',

  '<strong>Source year:</strong> ',
  featured_year,
  '<br>',

  '<strong>Transactions extracted:</strong> ',
  nrow(featured),

  '</p>',

  '<a class="ptr-button" href="',
  featured_pdf_url,
  '" target="_blank" rel="noopener">',
  'Open official House PDF',
  '</a>',

  '</div>',

  '<div class="ptr-pdf">',

  '<iframe ',
  'src="',
  featured_pdf_url,
  '#view=FitH" ',
  'title="Featured House PTR" ',
  'width="100%" ',
  'height="850px">',

  '</iframe>',

  '</div>'
)
```

### Extracted transactions from this PTR

```{r}
featured_table <- featured |>
  transmute(
    Owner = owner,
    Asset = asset_v8_2_cleaned,
    Ticker = ticker_v8_2_cleaned,
    Type = transaction_type,
    `Transaction date` = transaction_date,
    Amount = amount_category,
    `QA review` = review_level
  )

datatable(
  featured_table,
  rownames = FALSE,
  filter = "none",
  width = "100%",
  options = list(
    dom = "t",
    paging = FALSE,
    ordering = FALSE,
    autoWidth = TRUE
  )
)
```

The original disclosure above is the source document. The table beneath it shows the structured transaction records extracted from that same PTR.

---

## Explore the transactions

```{r}
explore_data <- ptr |>
  mutate(
    parsed_transaction_date = as.Date(
      transaction_date,
      format = "%Y-%m-%d"
    ),

    qa_norm = tolower(
      trimws(
        coalesce(review_level, "")
      )
    )
  ) |>
  filter(
    qa_norm != "high",
    !is.na(parsed_transaction_date),
    parsed_transaction_date >= as.Date("2021-01-01"),
    parsed_transaction_date <= Sys.Date()
  ) |>
  arrange(
    desc(parsed_transaction_date)
  )

representatives_count <- n_distinct(
  explore_data$politician[
    !is.na(explore_data$politician) &
    explore_data$politician != ""
  ]
)

assets_count <- n_distinct(
  explore_data$asset_v8_2_cleaned[
    !is.na(explore_data$asset_v8_2_cleaned) &
    explore_data$asset_v8_2_cleaned != ""
  ]
)

disclosures_count <- n_distinct(
  explore_data$filing_id[
    !is.na(explore_data$filing_id) &
    explore_data$filing_id != ""
  ]
)

transactions_count <- nrow(explore_data)
```

```{r, results='asis'}
cat(
  '<div class="explore-stats">',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Representatives</div>',
  '<div class="explore-stat-number count-up" data-target="',
  representatives_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Assets</div>',
  '<div class="explore-stat-number count-up" data-target="',
  assets_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Disclosures</div>',
  '<div class="explore-stat-number count-up" data-target="',
  disclosures_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Transactions</div>',
  '<div class="explore-stat-number count-up" data-target="',
  transactions_count,
  '">0</div>',
  '</div>',

  '</div>'
)
```

<script>
document.addEventListener("DOMContentLoaded", function () {

  const statSection = document.querySelector(".explore-stats");

  if (!statSection) {
    return;
  }

  let hasAnimated = false;

  function animateValue(element) {

    const target = Number(element.dataset.target);

    // Slower overall animation
    const duration = 3000;

    const startTime = performance.now();

    function update(currentTime) {

      const elapsed = currentTime - startTime;

      const progress = Math.min(
        elapsed / duration,
        1
      );

      /*
        Ease-in animation:
        starts very slowly,
        then accelerates toward the end.
      */
      const eased =
        Math.pow(progress, 2.4);

      const value = Math.floor(
        target * eased
      );

      element.textContent =
        value.toLocaleString();

      if (progress < 1) {

        requestAnimationFrame(update);

      } else {

        element.textContent =
          target.toLocaleString();

      }
    }

    requestAnimationFrame(update);
  }

  const observer = new IntersectionObserver(
    function(entries) {

      entries.forEach(function(entry) {

        if (
          entry.isIntersecting &&
          !hasAnimated
        ) {

          hasAnimated = true;

          document
            .querySelectorAll(".count-up")
            .forEach(animateValue);

          observer.disconnect();
        }

      });

    },
    {
      threshold: 0.35
    }
  );

  observer.observe(statSection);
});
</script>

The searchable table below contains the structured transaction records produced from the House PTR archive.

For the public-facing table, rows marked **high QA review** are excluded, malformed or future dates are removed, and the newest valid transactions appear first.

Use the search box or column filters to look for a politician, ticker, asset, district, transaction type, or date.

```{r}
display_data <- explore_data |>
  transmute(
    Politician = politician,
    District = state_district,
    `Transaction date` = transaction_date,
    `Notification date` = notification_date,
    Owner = owner,
    Asset = asset_v8_2_cleaned,
    Ticker = ticker_v8_2_cleaned,
    Type = transaction_type,
    Amount = amount_category,
    `QA review` = review_level,

    `House PDF` = ifelse(
      is.na(original_pdf_url) |
      original_pdf_url == "",

      "",

      paste0(
        '<a href="',
        original_pdf_url,
        '" target="_blank" rel="noopener">',
        'View PDF',
        '</a>'
      )
    )
  )

datatable(
  display_data,
  filter = "top",
  rownames = FALSE,
  escape = FALSE,
  width = "100%",

  options = list(
    pageLength = 10,

    lengthMenu = c(
      10,
      25,
      50,
      100
    ),

    scrollX = TRUE,
    scrollCollapse = TRUE,
    autoWidth = TRUE,
    searchHighlight = TRUE,

    order = list(
      list(2, "desc")
    )
  )
)
```

## Data source

The source records are official U.S. House Periodic Transaction Reports.

Each displayed transaction retains the original House disclosure URL when available.

:::