---
title: "Politician Stock Disclosures"
subtitle: "U.S. Senate Periodic Transaction Reports"
page-layout: full

format:
  html:
    toc: false

execute:
  echo: false
  warning: false
  message: false
---

<style>

/* =========================================================
   PAGE
   ========================================================= */

.quarto-title-block {
  display: none;
}

.wide-shell {
  width: min(1750px, calc(100vw - 32px));
  margin-left: auto;
  margin-right: auto;
}

.project-main-title {
  margin-bottom: 0.2rem;
}

.project-subtitle {
  font-size: 1.15rem;
  opacity: 0.7;
  margin-bottom: 1rem;
}

.dataTables_wrapper {
  font-size: 0.9rem;
}


/* =========================================================
   CHAMBER TOGGLE
   ========================================================= */

.chamber-toggle {
  display: inline-flex;
  gap: 0.5rem;
  margin-bottom: 1.5rem;
}

.chamber-toggle a,
.chamber-toggle span {
  padding: 0.35rem 0.9rem;

  border: 1px solid #6ea8fe;
  border-radius: 999px;

  font-size: 0.85rem;
  text-decoration: none;
  color: inherit;
}

.chamber-toggle .chamber-active {
  background: rgba(110, 168, 254, 0.18);
  font-weight: 700;
}

.chamber-toggle a:hover {
  background: rgba(110, 168, 254, 0.08);
}


/* =========================================================
   FEATURED PTR
   ========================================================= */

.featured-card {
  display: grid;

  grid-template-columns:
    minmax(560px, 0.9fr)
    minmax(0, 1.1fr);

  border: 1px solid #444;
  border-radius: 10px;
  overflow: hidden;

  margin: 1.25rem 0;
}

.featured-info {
  padding: 1.5rem;
  border-right: 1px solid #444;
}

.featured-info h3 {
  margin: 0 0 1.2rem 0;
}

.featured-meta {
  display: grid;
  gap: 0.65rem;
  margin-bottom: 1.35rem;
}

.featured-meta-row {
  display: grid;
  grid-template-columns: 115px 1fr;
  gap: 0.5rem;
  align-items: baseline;
}

.featured-meta-label {
  font-weight: 700;
}


/* =========================================================
   FEATURED CONTROLS
   ========================================================= */

.featured-controls {
  display: grid;

  grid-template-columns:
    240px minmax(250px, 1fr);

  gap: 1.25rem;

  align-items: start;

  max-width: 590px;

  margin-top: 1rem;
}

.featured-actions {
  display: grid;
  grid-template-columns: 1fr;

  gap: 0.65rem;

  width: 240px;
}

.ptr-button {
  display: flex;

  align-items: center;
  justify-content: center;

  width: 240px;
  height: 44px;

  box-sizing: border-box;

  padding: 0 0.9rem;

  border: 1px solid #6ea8fe;
  border-radius: 6px;

  background: transparent;
  color: inherit;

  text-decoration: none;
  text-align: center;

  white-space: nowrap;

  cursor: pointer;
  font: inherit;

  transition:
    border-color 0.15s ease,
    background 0.15s ease,
    transform 0.15s ease;
}

.ptr-button:hover {
  border-color: #9bc2ff;
  background: rgba(110, 168, 254, 0.08);
  transform: translateY(-1px);
}

.ptr-button[disabled],
.ptr-button.is-disabled {
  opacity: 0.45;
  cursor: default;
  pointer-events: none;
}


/* =========================================================
   FILING ID SEARCH
   ========================================================= */

.filing-search {
  width: 100%;

  padding-left: 1.2rem;

  border-left: 1px solid #444;
}

.filing-search label {
  display: block;

  margin-bottom: 0.55rem;

  font-size: 0.78rem;
  font-weight: 700;

  opacity: 0.75;
}

.filing-search-row {
  display: grid;

  grid-template-columns:
    minmax(0, 1fr) 72px;

  width: 100%;
}

.filing-search-row input {
  width: 100%;
  min-width: 0;

  height: 44px;

  box-sizing: border-box;

  padding: 0 0.7rem;

  border: 1px solid #555;
  border-right: none;

  border-radius: 6px 0 0 6px;

  background: transparent;
  color: inherit;

  font: inherit;
}

.filing-search-row input:focus {
  outline: none;
  border-color: #6ea8fe;
}

.filing-search-row button {
  height: 44px;

  box-sizing: border-box;

  border: 1px solid #6ea8fe;

  border-radius: 0 6px 6px 0;

  background: transparent;
  color: inherit;

  cursor: pointer;

  font: inherit;

  white-space: nowrap;
}

.filing-search-row button:hover {
  background: rgba(110, 168, 254, 0.08);
}

.filing-search-message {
  min-height: 1rem;

  margin-top: 0.45rem;

  font-size: 0.75rem;

  opacity: 0.7;
}


/* =========================================================
   FEATURED EXTRACTION TABLE
   ========================================================= */

.featured-extract {
  padding: 1.5rem;
  min-width: 0;
}

.featured-extract h3 {
  margin: 0 0 1rem 0;
}

.featured-table-wrap {
  width: 100%;
  overflow-x: auto;
}

.featured-table {
  width: 100%;
  border-collapse: collapse;
  font-size: 0.87rem;
}

.featured-table th,
.featured-table td {
  text-align: left;
  vertical-align: top;

  padding: 0.6rem 0.45rem;

  border-bottom: 1px solid #3b3b3b;
}

.featured-table th {
  opacity: 0.7;
  font-size: 0.75rem;
}

.featured-empty {
  opacity: 0.65;
  font-style: italic;
}


/* =========================================================
   NO-DATA PLACEHOLDER
   ========================================================= */

.no-data-card {
  padding: 1.5rem;

  border: 1px dashed #555;
  border-radius: 10px;

  margin: 1.25rem 0;

  opacity: 0.8;
}


/* =========================================================
   EXPLORE SUMMARY
   ========================================================= */

.explore-stats {
  display: grid;

  grid-template-columns:
    repeat(4, 1fr);

  margin: 1.5rem 0 2rem 0;

  border-top: 1px solid #3b3b3b;
  border-bottom: 1px solid #3b3b3b;
}

.explore-stat {
  padding: 1.2rem 1.4rem;

  border-right: 1px solid #3b3b3b;
}

.explore-stat:last-child {
  border-right: none;
}

.explore-stat-label {
  font-size: 0.72rem;

  text-transform: uppercase;

  letter-spacing: 0.08em;

  opacity: 0.55;

  margin-bottom: 0.35rem;
}

.explore-stat-number {
  font-size: 1.8rem;
  font-weight: 700;
  line-height: 1;
}


/* =========================================================
   RESPONSIVE
   ========================================================= */

@media (max-width: 1150px) {

  .featured-card {
    grid-template-columns: 1fr;
  }

  .featured-info {
    border-right: none;
    border-bottom: 1px solid #444;
  }
}

@media (max-width: 700px) {

  .wide-shell {
    width: calc(100vw - 24px);
  }

  .featured-controls {
    grid-template-columns: 1fr;
  }

  .featured-actions {
    width: 100%;
  }

  .ptr-button {
    width: 100%;
  }

  .filing-search {
    padding-left: 0;
    padding-top: 1rem;

    border-left: none;
    border-top: 1px solid #444;
  }

  .explore-stats {
    grid-template-columns: repeat(2, 1fr);
  }
}

@media (max-width: 500px) {

  .explore-stats {
    grid-template-columns: 1fr;
  }

  .explore-stat {
    border-right: none;
  }

  .featured-meta-row {
    grid-template-columns: 1fr;
    gap: 0;
  }
}

</style>


```{r}
library(readr)
library(dplyr)
library(DT)
library(jsonlite)


# Senate data lives in the sibling senate-ptr-scraper repo (source of
# truth for the automated scrape). Locally this is a real sibling folder;
# in CI, the deploy workflow checks that repo out into the same relative
# path so this works unchanged in both places.
data_path <- "../senate-ptr-scraper/data/03_transactions/senate_ptr_transactions_electronic.csv"

data_available <- file.exists(data_path)

if (data_available) {
  ptr_raw <- read_csv(data_path, show_col_types = FALSE)
  data_available <- nrow(ptr_raw) > 0
}


if (data_available) {

  ptr_prepared <- ptr_raw |>
    mutate(
      report_id = as.character(report_id),

      parsed_transaction_date =
        as.Date(transaction_date, format = "%Y-%m-%d"),

      owner_display = case_when(
        is.na(owner) | trimws(owner) == "" ~ "Self",
        toupper(trimws(owner)) == "SP" ~ "Spouse",
        toupper(trimws(owner)) == "JT" ~ "Joint",
        toupper(trimws(owner)) == "DC" ~ "Dependent child",
        TRUE ~ owner
      ),

      amount_display = coalesce(amount, "")
    )

} else {

  # Well-typed empty frame so every downstream chunk can run unchanged
  # (group_by/filter/transmute/datatable) even before the scraper has
  # ever produced data.
  ptr_prepared <- tibble(
    report_id = character(0),
    filer_name = character(0),
    office = character(0),
    filing_date = character(0),
    transaction_date = character(0),
    owner = character(0),
    asset_name = character(0),
    ticker = character(0),
    transaction_type = character(0),
    amount = character(0),
    report_url = character(0),
    parsed_transaction_date = as.Date(character(0)),
    owner_display = character(0),
    amount_display = character(0)
  )
}
```


::: {.column-screen}

::: {.wide-shell}


# Politician Stock Disclosures {.project-main-title}

<div class="project-subtitle">U.S. Senate Periodic Transaction Reports</div>

<div class="chamber-toggle">
<a href="stock-disclosures.qmd">House</a>
<span class="chamber-active">Senate</span>
</div>


This project turns official U.S. Senate **Periodic Transaction Report (PTR)** disclosures into structured transaction data that can be searched and analyzed. Electronic filings are scraped and parsed automatically; paper (scanned) filings are out of scope for now.


## Featured PTR


This section randomly selects one scraped Senate filing from the dataset.

Use **Show another PTR** to pick another example, or enter a **Report ID** to inspect a specific source disclosure.


```{r}
if (data_available) {

  filing_summary <- ptr_prepared |>
    group_by(
      report_id,
      filer_name,
      office,
      filing_date,
      report_url
    ) |>
    summarise(
      transaction_count = n(),
      .groups = "drop"
    ) |>
    filter(
      !is.na(report_id), report_id != "",
      !is.na(filer_name), filer_name != ""
    )

  featured_items <- lapply(seq_len(nrow(filing_summary)), function(i) {

    filing_info <- filing_summary[i, , drop = FALSE]

    filing_rows <- ptr_prepared |>
      filter(report_id == filing_info$report_id[[1]]) |>
      arrange(desc(parsed_transaction_date)) |>
      transmute(
        Owner = owner_display,
        Asset = asset_name,
        Ticker = ticker,
        Type = transaction_type,
        Date = transaction_date,
        Amount = amount_display
      )

    list(
      senator = filing_info$filer_name[[1]],
      office = filing_info$office[[1]],
      report_id = filing_info$report_id[[1]],
      filing_date = filing_info$filing_date[[1]],
      report_url = filing_info$report_url[[1]],
      transaction_count = nrow(filing_rows),
      transactions = filing_rows
    )
  })

} else {

  featured_items <- list()
}

featured_json <- toJSON(
  featured_items,
  auto_unbox = TRUE,
  dataframe = "rows",
  na = "null"
)
```


<div class="featured-card">

<div class="featured-info">

<h3 id="featured-name"></h3>

<div class="featured-meta">

<div class="featured-meta-row"><span class="featured-meta-label">State / Office</span><span id="featured-office"></span></div>

<div class="featured-meta-row"><span class="featured-meta-label">Report ID</span><span id="featured-report-id"></span></div>

<div class="featured-meta-row"><span class="featured-meta-label">Filing date</span><span id="featured-filing-date"></span></div>

<div class="featured-meta-row"><span class="featured-meta-label">Transactions</span><span id="featured-count"></span></div>

</div>


<div class="featured-controls">

<div class="featured-actions">
<button type="button" class="ptr-button" id="random-ptr-button">Show another PTR</button>
<a class="ptr-button" id="featured-filing-link" href="#" target="_blank" rel="noopener">View official Senate filing</a>
</div>

<div class="filing-search">
<label for="filing-id-search">Find by Report ID</label>
<div class="filing-search-row"><input id="filing-id-search" type="text" placeholder="e.g. 1a2b3c4d"><button id="filing-id-search-button" type="button">Load</button></div>
<div id="filing-search-message" class="filing-search-message"></div>
</div>

</div>

</div>


<div class="featured-extract">

<h3>Extracted transactions</h3>

<div class="featured-table-wrap">

<table class="featured-table">

<thead>
<tr>
<th>Owner</th>
<th>Asset</th>
<th>Ticker</th>
<th>Type</th>
<th>Date</th>
<th>Amount</th>
</tr>
</thead>

<tbody id="featured-table-body"></tbody>

</table>

</div>

</div>

</div>


```{r, results='asis'}
cat(
  '<script>',
  'const allFeaturedPTRs = ',
  featured_json,
  ';',
  '</script>'
)
```


<script>

(function () {

  let currentIndex = -1;

  function cleanValue(value) {
    if (value === null || value === undefined || value === "NA") {
      return "";
    }
    return String(value);
  }

  const hasData = Array.isArray(allFeaturedPTRs) && allFeaturedPTRs.length > 0;

  function randomIndex() {
    if (!hasData) {
      return -1;
    }

    if (allFeaturedPTRs.length <= 1) {
      return 0;
    }

    let nextIndex;

    do {
      nextIndex = Math.floor(Math.random() * allFeaturedPTRs.length);
    } while (nextIndex === currentIndex);

    return nextIndex;
  }

  function showNoDataState() {
    document.getElementById("featured-name").textContent = "No Senate PTR data yet";
    document.getElementById("featured-office").textContent = "";
    document.getElementById("featured-report-id").textContent = "";
    document.getElementById("featured-filing-date").textContent = "";
    document.getElementById("featured-count").textContent = "0";

    const link = document.getElementById("featured-filing-link");
    link.href = "#";
    link.classList.add("is-disabled");

    const tbody = document.getElementById("featured-table-body");
    tbody.innerHTML = "";

    const row = document.createElement("tr");
    const cell = document.createElement("td");
    cell.colSpan = 6;
    cell.className = "featured-empty";
    cell.textContent = "The automated scraper hasn't produced any Senate PTR data yet.";
    row.appendChild(cell);
    tbody.appendChild(row);
  }

  function renderFeaturedPTR(index) {
    currentIndex = index;

    const item = allFeaturedPTRs[index];

    document.getElementById("featured-name").textContent = cleanValue(item.senator);
    document.getElementById("featured-office").textContent = cleanValue(item.office);
    document.getElementById("featured-report-id").textContent = cleanValue(item.report_id);
    document.getElementById("featured-filing-date").textContent = cleanValue(item.filing_date);
    document.getElementById("featured-count").textContent = Number(item.transaction_count).toLocaleString();

    document.getElementById("filing-id-search").value = cleanValue(item.report_id);
    document.getElementById("filing-search-message").textContent = "";

    const link = document.getElementById("featured-filing-link");
    link.href = cleanValue(item.report_url) || "#";
    link.classList.remove("is-disabled");

    const tbody = document.getElementById("featured-table-body");
    tbody.innerHTML = "";

    let transactions = item.transactions;

    if (transactions && !Array.isArray(transactions)) {
      transactions = [transactions];
    }

    if (!transactions || transactions.length === 0) {
      const row = document.createElement("tr");
      const cell = document.createElement("td");
      cell.colSpan = 6;
      cell.className = "featured-empty";
      cell.textContent = "No extracted transaction rows.";
      row.appendChild(cell);
      tbody.appendChild(row);
    } else {
      transactions.forEach(function (transaction) {
        const row = document.createElement("tr");

        const values = [
          transaction.Owner,
          transaction.Asset,
          transaction.Ticker,
          transaction.Type,
          transaction.Date,
          transaction.Amount
        ];

        values.forEach(function (value) {
          const cell = document.createElement("td");
          cell.textContent = cleanValue(value);
          row.appendChild(cell);
        });

        tbody.appendChild(row);
      });
    }
  }

  function showRandomPTR() {
    if (!hasData) {
      showNoDataState();
      return;
    }
    renderFeaturedPTR(randomIndex());
  }

  function loadReportID() {
    if (!hasData) {
      return;
    }

    const input = document.getElementById("filing-id-search");
    const message = document.getElementById("filing-search-message");

    const requestedID = input.value.trim();

    if (!requestedID) {
      message.textContent = "Enter a Report ID.";
      return;
    }

    const index = allFeaturedPTRs.findIndex(function (item) {
      return String(item.report_id) === requestedID;
    });

    if (index === -1) {
      message.textContent = "Report ID not found in this dataset.";
      return;
    }

    message.textContent = "";
    renderFeaturedPTR(index);
  }

  function initializePTRFeature() {
    const randomButton = document.getElementById("random-ptr-button");
    const searchButton = document.getElementById("filing-id-search-button");
    const searchInput = document.getElementById("filing-id-search");

    randomButton.addEventListener("click", showRandomPTR);
    searchButton.addEventListener("click", loadReportID);

    searchInput.addEventListener("keydown", function (event) {
      if (event.key === "Enter") {
        loadReportID();
      }
    });

    showRandomPTR();
  }

  if (document.readyState === "loading") {
    document.addEventListener("DOMContentLoaded", initializePTRFeature);
  } else {
    initializePTRFeature();
  }

})();

</script>


---


## Explore the transactions


```{r}
explore_all <-
  ptr_prepared |>
  arrange(desc(parsed_transaction_date))

senators_count <- n_distinct(
  explore_all$filer_name[!is.na(explore_all$filer_name) & explore_all$filer_name != ""]
)

assets_count <- n_distinct(
  explore_all$asset_name[!is.na(explore_all$asset_name) & explore_all$asset_name != ""]
)

filings_count <- n_distinct(
  explore_all$report_id[!is.na(explore_all$report_id) & explore_all$report_id != ""]
)

transactions_count <- nrow(explore_all)
```


```{r, results='asis'}
cat(
  '<div class="explore-stats">',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Senators</div>',
  '<div class="explore-stat-number count-up" data-target="',
  senators_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Assets</div>',
  '<div class="explore-stat-number count-up" data-target="',
  assets_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Filings</div>',
  '<div class="explore-stat-number count-up" data-target="',
  filings_count,
  '">0</div>',
  '</div>',

  '<div class="explore-stat">',
  '<div class="explore-stat-label">Transactions</div>',
  '<div class="explore-stat-number count-up" data-target="',
  transactions_count,
  '">0</div>',
  '</div>',

  '</div>'
)
```


<script>

document.addEventListener("DOMContentLoaded", function () {
  const statSection = document.querySelector(".explore-stats");

  if (!statSection) {
    return;
  }

  let hasAnimated = false;

  function animateValue(element) {
    const target = Number(element.dataset.target);
    const duration = 4000;
    const startTime = performance.now();

    function update(currentTime) {
      const elapsed = currentTime - startTime;
      const progress = Math.min(elapsed / duration, 1);
      const eased = Math.pow(progress, 2.5);
      const value = Math.floor(target * eased);

      element.textContent = value.toLocaleString();

      if (progress < 1) {
        requestAnimationFrame(update);
      } else {
        element.textContent = target.toLocaleString();
      }
    }

    requestAnimationFrame(update);
  }

  const observer = new IntersectionObserver(
    function (entries) {
      entries.forEach(function (entry) {
        if (entry.isIntersecting && !hasAnimated) {
          hasAnimated = true;
          document.querySelectorAll(".count-up").forEach(animateValue);
          observer.disconnect();
        }
      });
    },
    { threshold: 0.35 }
  );

  observer.observe(statSection);
});

</script>


Use the global search box or individual column filters to search by report ID, senator, ticker, asset, state/office, transaction type, or date.


```{r}
if (data_available) {

  display_data <-
    explore_all |>
    transmute(
      `Report ID` = report_id,
      Senator = filer_name,
      `State / Office` = office,
      `Transaction date` = transaction_date,
      `Filing date` = filing_date,
      Owner = owner_display,
      Asset = asset_name,
      Ticker = ticker,
      Type = transaction_type,
      Amount = amount_display,
      `Senate filing` = report_url
    )

  datatable(
    display_data,
    filter = "top",
    rownames = FALSE,
    width = "100%",
    options = list(
      pageLength = 10,
      lengthMenu = c(10, 25, 50, 100),
      scrollX = TRUE,
      scrollCollapse = TRUE,
      autoWidth = TRUE,
      order = list(list(3, "desc")),
      columnDefs = list(
        list(
          targets = 10,
          orderable = FALSE,
          render = JS(
            "function(data, type, row, meta) {",
            "  if (type !== 'display') return data;",
            "  if (!data) return '';",
            "  return '<a href=\"' + data + '\" target=\"_blank\" rel=\"noopener\">View filing</a>';",
            "}"
          )
        )
      )
    )
  )

} else {

  htmltools::tags$div(
    class = "no-data-card",
    "No Senate PTR transactions have been scraped yet. Once the automated ",
    htmltools::tags$code("scrape-senate-ptrs"),
    " GitHub Action has run at least once, this table will populate automatically."
  )
}
```


## Data source


The source records are official U.S. Senate Periodic Transaction Reports, scraped from the Senate's Electronic Financial Disclosure (eFD) system.

Each displayed transaction retains a link to the original official Senate filing page. Paper (scanned) filings are not yet included.


:::

:::
