---
title: "Resume"
page-layout: full
title-block-banner: false

format:
  html:
    toc: false

execute:
  echo: false
  warning: false
  message: false
---

<style>

.quarto-title-block {
  display: none;
}

.resume-shell {
  width: min(820px, calc(100vw - 32px));
  margin-left: auto;
  margin-right: auto;
}

/* ---------------------------------------------------------
   HEADER
   --------------------------------------------------------- */

.resume-header {
  display: flex;
  justify-content: space-between;
  align-items: flex-start;
  gap: 1rem;

  border-bottom: 2px solid #6ea8fe;
  padding-bottom: 1rem;
  margin-bottom: 1.5rem;
}

.resume-name {
  font-size: 2rem;
  font-weight: 700;
  margin: 0;
}

.resume-tagline {
  opacity: 0.75;
  margin-top: 0.25rem;
}

.resume-contact {
  text-align: right;
  font-size: 0.9rem;
  white-space: nowrap;
}

.resume-contact a {
  color: inherit;
  text-decoration: none;
  border-bottom: 1px solid transparent;
}

.resume-contact a:hover {
  border-bottom-color: #6ea8fe;
}

.resume-contact div {
  margin-bottom: 0.25rem;
}

.resume-download {
  display: inline-flex;
  align-items: center;
  gap: 0.4rem;

  margin-top: 0.6rem;
  padding: 0.35rem 0.85rem;

  border: 1px solid #6ea8fe;
  border-radius: 6px;

  background: transparent;
  color: inherit;

  font: inherit;
  font-size: 0.85rem;
  cursor: pointer;

  transition: background 0.15s ease, transform 0.15s ease;
}

.resume-download:hover {
  background: rgba(110, 168, 254, 0.08);
  transform: translateY(-1px);
}

/* ---------------------------------------------------------
   SECTIONS
   --------------------------------------------------------- */

.resume-section {
  margin-bottom: 1.75rem;
}

.resume-section h2 {
  font-size: 1.05rem;
  text-transform: uppercase;
  letter-spacing: 0.06em;
  opacity: 0.75;

  border-bottom: 1px solid #3b3b3b;
  padding-bottom: 0.4rem;
  margin-bottom: 1rem;
}

.resume-summary {
  line-height: 1.55;
}

/* ---------------------------------------------------------
   EXPERIENCE / EDUCATION ENTRIES
   --------------------------------------------------------- */

.resume-entry {
  margin-bottom: 1.1rem;
  page-break-inside: avoid;
}

.resume-entry-head {
  display: flex;
  justify-content: space-between;
  align-items: baseline;
  gap: 1rem;
  flex-wrap: wrap;
}

.resume-entry-title {
  font-weight: 700;
}

.resume-entry-dates {
  font-size: 0.85rem;
  color: #6ea8fe;
  white-space: nowrap;
}

.resume-entry-org {
  opacity: 0.8;
  font-size: 0.92rem;
  margin-top: 0.1rem;
}

.resume-entry-bullets {
  margin: 0.5rem 0 0 0;
  padding-left: 1.2rem;
}

.resume-entry-bullets li {
  margin-bottom: 0.3rem;
  line-height: 1.45;
}

.resume-entry-details {
  font-size: 0.88rem;
  opacity: 0.75;
  margin-top: 0.15rem;
}

.resume-entry-link {
  font-size: 0.88rem;
  margin-top: 0.3rem;
}

.resume-entry-link a {
  color: #6ea8fe;
  text-decoration: none;
  word-break: break-all;
}

.resume-entry-link a:hover {
  text-decoration: underline;
}

/* ---------------------------------------------------------
   SKILLS
   --------------------------------------------------------- */

/* Pandoc wraps the raw `cat()` output (a run of inline <span> pills) in
   a <p> before it lands inside this div, so the flex rules that matter
   have to target that inner <p>, not the div itself -- otherwise the
   pills just wrap as ordinary inline text with a single space between
   them, which is why they visually crowd/touch. */
.resume-skills {
  display: flex;
  flex-wrap: wrap;
  row-gap: 0.75rem;
  column-gap: 0.85rem;
}

.resume-skills p {
  display: flex;
  flex-wrap: wrap;
  row-gap: 0.75rem;
  column-gap: 0.85rem;
  margin: 0;
}

.resume-skill-pill {
  display: inline-block;

  padding: 0.35rem 0.9rem;

  border: 1px solid #444;
  border-radius: 999px;

  font-size: 0.85rem;
  line-height: 1.2;
  white-space: nowrap;
}

/* ---------------------------------------------------------
   PRINT / PDF EXPORT
   --------------------------------------------------------- */

/* The browser's own print header/footer (page title, URL, date, page
   numbers) is a print-dialog setting, not something CSS can suppress --
   in Chrome/Edge, uncheck "Headers and footers" under "More settings"
   in the print dialog before saving as PDF. */
@page {
  size: letter;
  margin: 0.3in;
}

@media print {

  .navbar, #quarto-header, .footer, .page-footer, #quarto-footer,
  .quarto-back-to-top, .resume-download {
    display: none !important;
  }

  /* Quarto's page chrome adds its own padding/margin around the content
     area -- zero it out so the page margins above are the only margins
     in effect. It also uses a sticky-footer flex layout (min-height:
     100vh on the content grid) to push the site footer down, which adds
     a large block of empty vertical space that forces a spurious blank
     second printed page even after the footer itself is hidden -- cancel
     that here. */
  #quarto-content, #quarto-document-content, main.content {
    padding: 0 !important;
    margin: 0 !important;
  }

  html, body {
    height: auto !important;
    min-height: 0 !important;
    padding-top: 0 !important;
    margin-top: 0 !important;
  }

  #quarto-content {
    display: block !important;
    min-height: 0 !important;
    height: auto !important;
  }

  html, body {
    font-size: 10.5px;
  }

  body {
    line-height: 1.25;
  }

  p {
    margin: 0 0 0.3rem 0;
  }

  .resume-shell {
    width: 100%;
  }

  body {
    background: #fff !important;
    color: #000 !important;
  }

  .resume-header {
    margin-bottom: 0.35rem;
    padding-bottom: 0.2rem;
    border-bottom-color: #000;
  }

  .resume-name {
    font-size: 1.25rem;
  }

  .resume-tagline {
    margin-top: 0.05rem;
  }

  .resume-contact {
    font-size: 0.78rem;
  }

  .resume-contact div {
    margin-bottom: 0.1rem;
  }

  .resume-section {
    margin-bottom: 0.2rem;
  }

  .resume-section h2 {
    font-size: 0.75rem;
    margin-bottom: 0.2rem;
    padding-bottom: 0.1rem;
    border-bottom-color: #999;
    opacity: 1;
  }

  .resume-summary {
    margin: 0;
    line-height: 1.25;
  }

  .resume-entry {
    margin-bottom: 0.12rem;
  }

  .resume-entry-org {
    margin-top: 0.03rem;
  }

  .resume-entry-dates {
    color: #000;
  }

  .resume-entry-bullets {
    margin-top: 0.12rem;
  }

  .resume-entry-bullets li {
    margin-bottom: 0.03rem;
    line-height: 1.2;
  }

  .resume-entry-details {
    margin-top: 0.03rem;
  }

  .resume-skills, .resume-skills p {
    row-gap: 0.25rem;
    column-gap: 0.4rem;
  }

  .resume-skill-pill {
    padding: 0.1rem 0.5rem;
    border-color: #999;
  }

  .resume-entry-link {
    font-size: 0.7rem;
    margin-top: 0.12rem;
  }

  a {
    color: #000 !important;
  }
}

/* ---------------------------------------------------------
   RESPONSIVE
   --------------------------------------------------------- */

@media (max-width: 600px) {

  .resume-header {
    flex-direction: column;
  }

  .resume-contact {
    text-align: left;
  }
}

</style>


```{r}
library(yaml)
library(glue)
library(purrr)

resume <- read_yaml("data/resume.yml")

format_dates <- function(start, end = "") {
  if (is.null(end) || !nzchar(end) || identical(start, end)) {
    return(as.character(start))
  }
  glue("{start} – {end}")
}

render_bullets <- function(bullets) {
  if (length(bullets) == 0) {
    return("")
  }
  items <- paste0("<li>", bullets, "</li>", collapse = "")
  glue('<ul class="resume-entry-bullets">{items}</ul>')
}

render_entry <- function(title, org, location, start, end, bullets = character(0), details = "") {
  org_line <- if (nzchar(location)) glue("{org} — {location}") else org

  details_html <- if (nzchar(details)) {
    glue('<div class="resume-entry-details">{details}</div>')
  } else {
    ""
  }

  # Built as a single line (no leading whitespace on wrapped lines) --
  # Pandoc treats 4+ leading spaces as an indented code block, so any
  # multi-line indented HTML here would get escaped instead of rendered.
  paste0(
    '<div class="resume-entry">',
    '<div class="resume-entry-head">',
    '<div class="resume-entry-title">', title, '</div>',
    '<div class="resume-entry-dates">', format_dates(start, end), '</div>',
    '</div>',
    '<div class="resume-entry-org">', org_line, '</div>',
    details_html,
    render_bullets(bullets),
    '</div>'
  )
}

render_project <- function(title, year, bullets = character(0), url = "") {
  link_html <- if (nzchar(url)) {
    glue('<div class="resume-entry-link"><a href="{url}" target="_blank" rel="noopener">{url}</a></div>')
  } else {
    ""
  }

  paste0(
    '<div class="resume-entry">',
    '<div class="resume-entry-head">',
    '<div class="resume-entry-title">', title, '</div>',
    '<div class="resume-entry-dates">', year, '</div>',
    '</div>',
    render_bullets(bullets),
    link_html,
    '</div>'
  )
}

experience_html <- resume$experience |>
  map_chr(~ render_entry(.x$title, .x$org, .x$location, .x$start, .x$end, .x$bullets)) |>
  paste(collapse = "\n")

volunteer_html <- resume$volunteer |>
  map_chr(~ render_entry(.x$title, .x$org, .x$location, .x$start, .x$end, .x$bullets)) |>
  paste(collapse = "\n")

projects_html <- resume$projects |>
  map_chr(~ render_project(.x$title, .x$year, .x$bullets, .x$url)) |>
  paste(collapse = "\n")

education_html <- resume$education |>
  map_chr(~ render_entry(.x$degree, .x$school, .x$location, .x$start, .x$end, details = .x$details)) |>
  paste(collapse = "\n")

skills_html <- resume$skills |>
  map_chr(~ glue('<span class="resume-skill-pill">{.x}</span>')) |>
  paste(collapse = "\n")
```


::: {.resume-shell}

<div class="resume-header">

<div>
<p class="resume-name">`r resume$name`</p>
<div class="resume-tagline">`r resume$tagline`</div>
</div>

<div class="resume-contact">
<div><a href="mailto:`r resume$contact$email`">`r resume$contact$email`</a></div>
<div><a href="`r resume$contact$github`" target="_blank" rel="noopener">GitHub</a></div>
<button type="button" class="resume-download" onclick="window.print()" title="Opens your browser's print dialog — choose Save as PDF">Print / Save as PDF</button>
</div>

</div>


<div class="resume-section">
<h2>Summary</h2>
<p class="resume-summary">`r trimws(resume$summary)`</p>
</div>


<div class="resume-section">
<h2>Experience</h2>
```{r, results='asis'}
cat(experience_html)
```
</div>


<div class="resume-section">
<h2>Volunteer Experience</h2>
```{r, results='asis'}
cat(volunteer_html)
```
</div>


<div class="resume-section">
<h2>Projects</h2>
```{r, results='asis'}
cat(projects_html)
```
</div>


<div class="resume-section">
<h2>Education</h2>
```{r, results='asis'}
cat(education_html)
```
</div>


<div class="resume-section">
<h2>Skills</h2>
<div class="resume-skills">
```{r, results='asis'}
cat(skills_html)
```
</div>
</div>

:::
